Appendix S1: Supporting Information

### 2021-09-03 ms/SI.Rmd
Lighten lines in map

```{r protected-map, fig.width = 7, fig.height = 9}
# Define function to make maps showing overlap of protected areas and grid-cells with high biodiversity
# These depend on various objects being in the current environment!
# pass the dots to filter data
make_protected_plot <- function(part, variable, ...) {
  ggplot() +
    geom_sf(data = japan, lwd = 0.10, fill = "white") +
    geom_sf(data = protected_areas %>% mutate(status = str_to_sentence(status)), aes(fill = status), color = "transparent") +
    geom_sf(
      data = biodiv_ferns_spatial %>% filter(...), 
      fill = "transparent", color = "black", lwd = 0.20) +
    annotate(
      geom="richtext", y = Inf, x = -Inf, 
      label = glue("<span style='color:black'>**({part})** {variable}</span>"), 
      hjust = "inward", vjust = "inward", color = "white") +
    scale_fill_manual(values = protection_cols, name = "Protection status") +
    scale_x_continuous(breaks = c(125, 135, 145)) +
    scale_y_continuous(breaks = c(25, 35, 45)) +
    map_theme()
}

@@

```{r deer-map, fig.width = 7, fig.height = 9}
# Define function to make maps showing overlap of areas with deer and grid-cells with high biodiversity
# These depend on various objects being in the current environment!
make_deer_plot <- function(part, variable, ...) {
  ggplot() +
    geom_sf(data = japan, lwd = 0.10, fill = "white") +
    geom_sf(data = deer_range %>% filter(range == "estimated") %>% mutate(range = str_to_sentence(range)), aes(fill = range), color = "transparent") +
    geom_sf(data = deer_range %>% filter(range == "2003"), aes(fill = range), color = "transparent") +
    geom_sf(data = deer_range %>% filter(range == "1978"), aes(fill = range), color = "transparent") +
    geom_sf(
      data = biodiv_ferns_spatial %>% filter(...), 
      fill = "transparent", color = "black", lwd = 0.20) +
    annotate(
      geom="richtext", y = Inf, x = -Inf, 
      label = glue("<span style='color:black'>**({part})** {variable}</span>"), 
      hjust = "inward", vjust = "inward", color = "white") +
    scale_fill_manual(values = deer_cols, name = "Range data source") +
    scale_x_continuous(breaks = c(125, 135, 145)) +
    scale_y_continuous(breaks = c(25, 35, 45)) +
    map_theme()
}

>>>>

```{r protected-map, fig.width = 7, fig.height = 9}
# Define function to make maps showing overlap of protected areas and grid-cells with high biodiversity
# These depend on various objects being in the current environment!
# pass the dots to filter data
make_protected_plot <- function(part, variable, ...) {
  ggplot() +
    geom_sf(data = japan, lwd = 0.07, fill = "white") +
    geom_sf(data = protected_areas %>% mutate(status = str_to_sentence(status)), aes(fill = status), color = "transparent") +
    geom_sf(
      data = biodiv_ferns_spatial %>% filter(...), 
      fill = "transparent", color = "black", lwd = 0.12) +
    annotate(
      geom="richtext", y = Inf, x = -Inf, 
      label = glue("<span style='color:black'>**({part})** {variable}</span>"), 
      hjust = "inward", vjust = "inward", color = "white") +
    scale_fill_manual(values = protection_cols, name = "Protection status") +
    scale_x_continuous(breaks = c(125, 135, 145)) +
    scale_y_continuous(breaks = c(25, 35, 45)) +
    map_theme()
}

@@

```{r deer-map, fig.width = 7, fig.height = 9}
# Define function to make maps showing overlap of areas with deer and grid-cells with high biodiversity
# These depend on various objects being in the current environment!
make_deer_plot <- function(part, variable, ...) {
  ggplot() +
    geom_sf(data = japan, lwd = 0.07, fill = "white") +
    geom_sf(data = deer_range %>% filter(range == "estimated") %>% mutate(range = str_to_sentence(range)), aes(fill = range), color = "transparent") +
    geom_sf(data = deer_range %>% filter(range == "2003"), aes(fill = range), color = "transparent") +
    geom_sf(data = deer_range %>% filter(range == "1978"), aes(fill = range), color = "transparent") +
    geom_sf(
      data = biodiv_ferns_spatial %>% filter(...), 
      fill = "transparent", color = "black", lwd = 0.12) +
    annotate(
      geom="richtext", y = Inf, x = -Inf, 
      label = glue("<span style='color:black'>**({part})** {variable}</span>"), 
      hjust = "inward", vjust = "inward", color = "white") +
    scale_fill_manual(values = deer_cols, name = "Range data source") +
    scale_x_continuous(breaks = c(125, 135, 145)) +
    scale_y_continuous(breaks = c(25, 35, 45)) +
    map_theme()
}
